From Freebase to Wikidata: The Great Migration

### 2015-10-13 paper.tex
Reworked Section 6.

From the Freebase dump we have been able to create more than 17M~Wikidata claims
(\emph{i.e.}, statement without references) including 1.5M~IDs.
For that we have used 31M~facts.
When we add some references we get 19.6M~statements, and, after removing 1M~of duplicates
and the ones already in Wikidata, we obtain 14M~new statements.
So, if all these statements were added to Wikidata,
it would lead to a~21\% increase of Wikidata statements number.
But why are these numbers so low compared to the size of Freebase?
We believe that the main reason is that we have only mapped to Wikidata 4.56M~items, (\emph{i.e.},
only 9.5\% of Freebase topics), that are the subject of only 64M~facts.
So, we could not hope to map more than 64M~statements
assuming that we could map all reverse properties, and we couldn't.
So, assuming that we do not care about the not mapped topics,
we have created a~statement for more than 24\% of the facts.
If we restrict ourselves to the reviewed facts, a~set of 1.6M~facts
that have been human curated, we have far better results.
There are 0.58M~facts which subjects are mapped to Wikidata and 0.52M~of them
(\emph{i.e.}, 92\%) are converted into Wikidata statements.
58\% of the statements created from reviewed fact are already in Wikidata,
allowing us to add 0.25M~of new reviewed statements to Wikidata.

@@

We believe that the main way of improvements is to extend the migration to more Freebase topics
by suggesting Wikidata users to create new Wikidata items.
A possible way of doing it is to create a~small gamified user interface that would allow users
to create new Wikidata items for a~suggested topic or to add map them to an existing Wikidata item.
In order to suggest interesting topics to add to Wikidata
we could rank the not mapped yet topics per number of incoming links from already mapped topic
and filter not interesting types like ISBNs.
Another way of improvement is to upload using a~bot high quality datasets,
like the reviewed facts or some sets,
for external ids in order to speed up the integration of Freebase content into Wikidata.
We have already started to upload the simple reviewed facts about humans
like birth date, death place or gender using a~bot.
We have also started to investigate on importing some labels
that are in Freebase and are missing in Wikidata.
In the 17.2M~of Freebase labels for mapped topics only 0.9M, \emph{i.e.},
5\%, are missing in Wikidata.

We have been able in a~fairly short amount of time to provide to the Wikidata community
more than 14M~of new Wikidata statements using a~new tool
well integrated into the Wikidata user interface.
The effort needed to map two fairly different knowledge bases has also been a~good occasion
to highlight the difficulty to have good metrics to measure the size
and, so, the ``value'', of such databases.
We hope that this project will allow to increase the completeness of Wikidata and,
helped by the comparison to another database, to improve its quality.

>>>>

From the Freebase dump, we have been able to create more than 17M~Wikidata claims
(\emph{i.e.}, statements without references), including 1.5M~IDs.
For that, we have used 31M~Freebase facts.
With additional references, we obtain 19.6M~statements, and, after removing 1M~duplicates
and facts already contained in Wikidata, we obtain 14M~new statements.
Thus, if all these statements were added to Wikidata,
this would lead to a~21\% increase of the number of statements in Wikidata.
The question raises why these numbers are so low compared to the size of Freebase.
We argue that the main reason is that we have only mapped 4.56M~items to Wikidata,
\emph{i.e.}, only 9.5\% of Freebase's topics in total, which are the subject of only 64M~facts.
Even under ideal circumstances, we cannot map more than 64M~statements,
and this is assuming that we could map all reverse properties, which, in fact, we could not.
So leaving aside the not mapped topics, we have created a~statement for more than 24\% of the facts.
If we restrict ourselves to reviewed facts---a~set of 1.6M~human curated facts---we have far better results.
There are 0.58M~facts whose subjects are mapped to Wikidata, and 0.52M~of them
(\emph{i.e.}, 92\%) are converted to Wikidata statements.
58\% of the statements created from reviewed fact are already in Wikidata,
allowing us to add 0.25M~of new reviewed statements to Wikidata.

@@

We reckon that the most improvements can be achieved
by extending the migration to more Freebase topics
by suggesting Wikidata users to create new Wikidata items.
A~possible way of realizing this is to create a~user interface%
---possibly leveraging elements of gamification---%
that would allow users to create new Wikidata items for a~suggested topic
or to add a~mapping for them to an existing Wikidata item.
In order to suggest interesting topics to add to Wikidata,
we could rank the not mapped yet topics per number of incoming links
from already mapped topics and filter less interesting types like ISBNs.
Another area for improvement is to upload high quality datasets using a~bot,
like the reviewed facts or some sets for external IDs,
in order to speed up the integration of Freebase content into Wikidata.
We have already started to upload simple reviewed facts about humans
like birth date, death place or gender using a~bot.
We have also begun to import labels that are in Freebase and are absent from Wikidata.
In the 17.2M~Freebase labels for mapped topics, only 0.9M, \emph{i.e.}, 5\%, are missing in Wikidata.

Concluding, in a~fairly short amount of time, we have been able
to provide to the Wikidata community more than 14M~new Wikidata statements
using a~novel customizable and generalizable software solution called Primary Sources Tool
that is well integrated into the Wikidata user interface.
The effort needed to map two fairly different knowledge bases has also been a~good occasion
to highlight the difficulty of having good metrics to measure the size
and in consequence the ``value'' of such collaborative knowledge bases.
We envision that this project now with Freebase, and for even more datasets in the future,
will facilitate to increase the completeness of Wikidata.
